### 2020-04-28 README.Rmd
Update results for Leeds

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis")
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()

>>>>

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(14, 15)) + tm_scale_bar()
